Gentoo Package Dependencies over Time

### 2014-08-07 Paper/paper.tex
Added results table

\begin{figure}
\centering
\includegraphics[width=\linewidth]{depgraph.pdf}
\caption{Example dependency graph.}\label{fig:depgraph-chat}
\vspace{-1em}
\end{figure}

No software project stands entirely on its own. Software is usually developed by taking one or more existing libraries of components and combining those components in ways to create new products. Take for example a simple chat application. The chat application uses a different library for user interface development that provides components such as a window a text entry field and a button (that is labeled "send message" by the chat application). This user interface library in its turn uses a graphics library to draw the lines, rectangles and text necessary for the fields and buttons. The graphics library uses a library to read font files and uses the fonts to turn text into pictures that can be displayed on the screen. The graphics library then sends the contents of the window to the window manager, which in turns uses a graphics card driver to instruct the hardware. The chat application uses a networking library to provide it with the basic components for internet communication and uses a file library to store the users settings. The same file library is also used by the font library to read font files. The dependency graph so described is drawn in figure~\ref{fig:depgraph-chat}. Compared to a real chat application the graph is hugely simplified, tracing a real chat application back to all the components involved will likely result in hundreds of libraries used.

@@

\section{Related work}

@@

\begin{figure}\small\centering
\caption[Bass model of innovation diffusion]{The Bass model of innovation diffusion. The blue trace represents a Bass diffusion with $p=0.01$ and $q=0.90$. The purple trace bass diffusion with $p=0.90$ and $q=0.01$.}
\label{fig:bass}
\includegraphics{Bass.pdf}
\end{figure}

@@

\begin{table}\centering\small
\caption[Bass model variables and parameters]{Overview of the variables and parameters of the Bass model as presented in equation~\eqref{eq:bass-model}.}
\label{tbl:bass-model}
\begin{tabular}{cll}
\toprule
& Dimension & description \\
\midrule
$A$   & adopters    & adopters at a the model time \\
$t$   & time        & model time \\
\midrule
$t_0$ & time        & time of innovation introduction \\
$M$   & adopters    & number of potential adopters \\
$p$   & time$^{-1}$ & rate of adopter innovation \\
$q$   & time$^{-1}$ & rate of adopter imitation \\
\bottomrule
\end{tabular}
\end{table}

@@

Special tools where developed to extract the time series of the number of adopters $A_t$ for a given package. This time series was then fit to \eqref{eq:bass} using Mathematica's \texttt{NonLinearModelFit}. The goodness-of-fit was analysed using an ANOVA table and calculated using the adjust coefficient of determination $\bar{R}^2$. The parameters were extracted from the fit, and confidence intervals were calculated under assumptions of normality. In \ref{tbl:results} the relevant parameters are presented with their mean value and a $95\%$ confidence interval. Since normality was assumed, the confidence intervals ignore the $p \ge 0$ and $q \ge 0$ constraints.

@@

\begin{figure}[t]
\begin{alltt}
>=media-libs/taglib-1.6.1[asf,mp4]
>=media-libs/taglib-extras-1.0.1
player? (
    app-crypt/qca:2
    >=app-misc/strigi-0.5.7[dbus,qt4]
    || ( >=dev-db/mysql-5.0.76
         =virtual/mysql-5.1 )
    >=kde-base/kdelibs-4.3[opengl?,semantic-desktop?]
    sys-libs/zlib
    x11-libs/qt-script
    >=x11-libs/qtscriptgenerator-0.1.0
\end{alltt}
\vspace{-1em}
\caption{Fragment of the runtime dependencies of the Amarok music player.}\label{fig:amarokruntime}
\vspace{-2em}
\end{figure}

@@

@@

\begin{table}
\centering
\caption{Key figures of the dataset}\label{tbl:dataset}
\begin{tabular}{ll}
\toprule
\multicolumn{2}{c}{\emph{Time}} \\[0.5mm]
Period & 2000 to Q1 2012 \\
Resolution & Monthly \\
Snapshots & 154 Graphs \\
\midrule
\multicolumn{2}{c}{\emph{All graphs}} \\[0.5mm]
Nodes & 1.3 Million \\
Vertices & 6.9 Million \\
\midrule
\multicolumn{2}{c}{\emph{Final graph}} \\[0.5mm]
Nodes & 15 Thousand \\
Vertices & 80 Thousand \\
\midrule
\multicolumn{2}{c}{\emph{Raw ebuilds}} \\[0.5mm]
Format & SquashFS \\
Size & 239 MB (compressed) \\
 & 4.4 GB (uncompressed) \\
Files & 2,990,722 \\
\midrule
\multicolumn{2}{c}{\emph{Compressed graphs}} \\[0.5mm]
Format & Tar+XZ compressed GML \\
Size & 2 MB \\
\bottomrule
\end{tabular}
\end{table}

\section{Exploring the Dataset}

\begin{figure}
\centering
\subfigure[Total number of packages]{\includegraphics[width=0.45\textwidth]{packageCountUnfiltered2.pdf}\label{fig:pkgsgrowth}}
\subfigure[Additions and removals]{\includegraphics[width=0.45\textwidth]{packageCountDeltaUnfiltered2.pdf}\label{fig:pkgsgrowthdelta}}
\caption{Growth of the Gentoo package database over time.}\label{fig:pkgsgrowth}
\end{figure}

@@

\begin{figure}
\centering
\subfigure[Dependencies per package]{\includegraphics[width=0.45\textwidth]{histo-out.pdf}\label{fig:dephisto-out}}
\subfigure[Dependers per package]{\includegraphics[width=0.45\textwidth]{histo-in.pdf}\label{fig:dephisto-in}}
\caption{Double logarithmic histograms of the number of incoming and outgoing dependencies per package.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[clip,trim=0 0 1cm 10cm,width=\linewidth]{kde.pdf}
\caption{Internal dependencies of modules in the KDE project. Color represents the $k$-core measure. The graph edges have been bundled to improve readability.}\label{fig:kde2}
\end{figure}

@@

From the entire list of packages, a few well-known (at least according to the author) packages where selected. The selection criteria was that the package must not have existed before (around) 2004, because the Gentoo Portage database was still too immature then, and the package must have gained a considerable number of dependers since its introduction. In \ref{tbl:results}, we list some selected packages along with their parameters. In all cases the adjusted coefficient of determination $\bar{R}^2$ was more than $99\%$.

\begin{table}
\centering
\caption{Results of fitting the Bass model.}\label{tbl:results}
\begin{tabular}{lr@{ $\pm$}rr@{ $\pm$}rr@{ $\pm$}r}
\toprule
Package & \multicolumn{2}{c}{$p$} & \multicolumn{2}{c}{$q$} & \multicolumn{2}{c}{$M$} \\
\midrule
\texttt{git}         & 0.00 & 0.01    & 0.73 & 0.13   & 746 & 394 \\
\texttt{libnotify}   & 0.05 & 0.08    & 0.72 & 0.30   & 103 &   9 \\
\texttt{udev}        & 0.01 & 0.01    & 0.50 & 0.12   & 200 &  65 \\
\texttt{cairo}       & 0.01 & 0.01    & 0.43 & 0.09   & 249 &  44 \\
\texttt{libmad}      & 0.18 & 0.14    & 1.13 & 0.3    &  55 &   1 \\
\texttt{libtheora}   & 0.11 & 0.09    & 0.63 & 0.21   &  32 &   1 \\
\texttt{taglib}      & 0.22 & 0.03    & 0.04 & 0.06   &  62 &  12 \\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{BassFit-git2.pdf}
\vspace{-2em}
\caption{The imitation driven adoption of \texttt{git}.}\label{fig:git}
\vspace{-1.5em}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{BassFit-libmad2.pdf}
\vspace{-2em}
\caption{The innovation driven adoption of \texttt{libmad}.}\label{fig:libmad}
\vspace{-1em}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{BassFit-xulrunner-22.pdf}
\vspace{-2em}
\caption{The rise and decline of \texttt{xulrunner}.}\label{fig:xulrunner}
\vspace{-1em}
\end{figure}

@@

Excluding the blue dots from the data results in the Bass model fit from figure \ref{fig:xulrunner}. The fitness increases to $\bar{R}^2=99.54\%$ and the parameters have tighter and reasonable confidence intervals. This is strong evidence that the initial adoption of the package is a Bass diffusion process. To explain the last part, the model should be extended with an obsolescence term.

@@

@@

\begin{table}
\caption{The ten selected packages}\label{tbl:selected}
\begin{tabular}{rlp{20em}}
\toprule
Growth & Package & Description \\
\midrule
\raisebox{-.15em}{\includegraphics[height=.8em]{sparkline-34-dev-dotnet-gconf-sharp.pdf}} & \texttt{dev-dotnet/gconf-sharp} & GtkSharp's gconf module \\
\raisebox{-.15em}{\includegraphics[height=.8em]{sparkline-65-dev-haskell-cabal.pdf}}  & \texttt{dev-haskell/cabal} & Framework for packaging Haskell software \\
\raisebox{-.15em}{\includegraphics[height=.8em]{sparkline-218-dev-libs-libunique.pdf}}  & \texttt{dev-libs/libunique} & Library for writing single instance application \\
\raisebox{-.15em}{\includegraphics[height=.8em]{sparkline-77-dev-python-lxml.pdf}}  & \texttt{dev-python/lxml} & Python bindings for libxml2 and libxslt \\
\raisebox{-.15em}{\includegraphics[height=.8em]{sparkline-157-dev-python-simplejson.pdf}}  & \texttt{dev-python/simplejson} & JSON encoder/decoder for Python \\
\raisebox{-.15em}{\includegraphics[height=.8em]{sparkline-240-dev-vcs-git.pdf}}  & \texttt{dev-vcs/git} & The stupid content tracker \\
\raisebox{-.15em}{\includegraphics[height=.8em]{sparkline-242-dev-vcs-mercurial.pdf}}  & \texttt{dev-vcs/mercurial} & Scalable distributed SCM \\
\raisebox{-.15em}{\includegraphics[height=.8em]{sparkline-17-gnome-base-gnome-keyring.pdf}}  & \texttt{gnome-base/gnome-keyring} & Password and keyring managing daemon \\
\raisebox{-.15em}{\includegraphics[height=.8em]{sparkline-206-media-libs-libcanberra.pdf}} & \texttt{media-libs/libcanberra} & Portable sound event library \\
\raisebox{-.15em}{\includegraphics[height=.8em]{sparkline-143-x11-misc-xdg-utils.pdf}} & \texttt{x11-misc/xdg-utils} & Portland utils for interoperability \\
\bottomrule
\end{tabular}
\end{table}
% IDs = {34, 65, 218, 77, 157, 240, 242, 17, 206, 143}

@@

@@

\begin{figure}
\centering
% 34, 65, 218, 77, 157, 240, 242, 17, 206, 143
\subfigure[\texttt{dev-dotnet/gconf-sharp}]{\includegraphics[width=0.45\textwidth]{BassFit-34-dev-dotnet-gconf-sharp.pdf}\label{fig:fit34}}
\subfigure[\texttt{dev-haskell/cabal}]{\includegraphics[width=0.45\textwidth]{BassFit-65-dev-haskell-cabal.pdf}\label{fig:fit65}}
\subfigure[\texttt{dev-libs/libunique}]{\includegraphics[width=0.45\textwidth]{BassFit-218-dev-libs-libunique.pdf}\label{fig:fit218}}
\subfigure[\texttt{dev-python/lxml}]{\includegraphics[width=0.45\textwidth]{BassFit-77-dev-python-lxml.pdf}\label{fig:fit77}}
\subfigure[\texttt{dev-python/simplejson}]{\includegraphics[width=0.45\textwidth]{BassFit-157-dev-python-simplejson.pdf}\label{fig:fit157}}
\subfigure[\texttt{dev-vcs/git}]{\includegraphics[width=0.45\textwidth]{BassFit-240-dev-vcs-git.pdf}\label{fig:fit240}}
\subfigure[\texttt{dev-vcs/mercurial}]{\includegraphics[width=0.45\textwidth]{BassFit-242-dev-vcs-mercurial.pdf}\label{fig:fit242}}
\subfigure[\texttt{gnome-base/gnome-keyring}]{\includegraphics[width=0.45\textwidth]{BassFit-17-gnome-base-gnome-keyring.pdf}\label{fig:fit17}}
\subfigure[\texttt{media-libs/libcanberra}]{\includegraphics[width=0.45\textwidth]{BassFit-206-media-libs-libcanberra.pdf}\label{fig:fit206}}
\subfigure[\texttt{x11-misc/xdg-utils}]{\includegraphics[width=0.45\textwidth]{BassFit-143-x11-misc-xdg-utils.pdf}\label{fig:fit143}}
\caption{Bass curve fits on ten randomly selected packages that met the criteria.}
\end{figure}

@@

\section{Relevance — Implications to practice and research}

>>>>

No software project stands entirely on its own. Software is usually developed by taking one or more existing libraries of components and combining those \begin{wrapfigure}{r}{0.5\linewidth}
\small\centering
\includegraphics[width=\linewidth]{depgraph.pdf}
\caption{Example dependency graph.}\label{fig:depgraph-chat}
\vspace{-1em}
\end{wrapfigure}
components in ways to create new products. Take for example a simple chat application. The chat application uses a different library for user interface development that provides components such as a window a text entry field and a button (that is labeled "send message" by the chat application). This user interface library in its turn uses a graphics library to draw the lines, rectangles and text necessary for the fields and buttons. The graphics library uses a library to read font files and uses the fonts to turn text into pictures that can be displayed on the screen. The graphics library then sends the contents of the window to the window manager, which in turns uses a graphics card driver to instruct the hardware. The chat application uses a networking library to provide it with the basic components for internet communication and uses a file library to store the users settings. The same file library is also used by the font library to read font files. The dependency graph so described is drawn in figure~\ref{fig:depgraph-chat}. Compared to a real chat application the graph is hugely simplified, tracing a real chat application back to all the components involved will likely result in hundreds of libraries used.

@@

\section{Related Work}

@@

\begin{wrapfigure}{r}{0.5\linewidth}
\small\centering
\includegraphics[width=\linewidth]{Bass.pdf}
\caption[Bass model of innovation diffusion]{The Bass model of innovation diffusion. The blue trace represents a Bass diffusion with $p=0.01$ and $q=0.90$. The purple trace bass diffusion with $p=0.90$ and $q=0.01$.}
\label{fig:bass}
\end{wrapfigure}

@@

\begin{table}
\centering\small
\caption[Bass model variables and parameters]{Overview of the variables and parameters of the Bass model as presented in equation~\eqref{eq:bass-model}.}
\label{tbl:bass-model}
\begin{tabular}{cll}
\toprule
& Dimension & description \\
\midrule
$A$   & adopters    & adopters at a the model time \\
$t$   & time        & model time \\
\midrule
$t_0$ & time        & time of innovation introduction \\
$M$   & adopters    & number of potential adopters \\
$p$   & time$^{-1}$ & rate of adopter innovation \\
$q$   & time$^{-1}$ & rate of adopter imitation \\
\bottomrule
\end{tabular}
\end{table}

@@

Special tools where developed to extract the time series of the number of adopters $A_t$ for a given package. This time series was then fit to \eqref{eq:bass} using Mathematica's \texttt{NonLinearModelFit}. The goodness-of-fit was analysed using an ANOVA table and calculated using the adjust coefficient of determination $\overline{R}^2$. The parameters were extracted from the fit, and confidence intervals were calculated under assumptions of normality. In \ref{tbl:results} the relevant parameters are presented with their mean value and a $95\%$ confidence interval. Since normality was assumed, the confidence intervals ignore the $p \ge 0$ and $q \ge 0$ constraints.

@@

\begin{figure}[t]
\small\centering
\begin{alltt}
>=media-libs/taglib-1.6.1[asf,mp4]
>=media-libs/taglib-extras-1.0.1
player? (
    app-crypt/qca:2
    >=app-misc/strigi-0.5.7[dbus,qt4]
    || ( >=dev-db/mysql-5.0.76
         =virtual/mysql-5.1 )
    >=kde-base/kdelibs-4.3[opengl?,semantic-desktop?]
    sys-libs/zlib
    x11-libs/qt-script
    >=x11-libs/qtscriptgenerator-0.1.0
\end{alltt}
\vspace{-1em}
\caption{Fragment of the runtime dependencies of the Amarok music player.}\label{fig:amarokruntime}
\vspace{-2em}
\end{figure}

@@

\begin{wraptable}{r}{0.5\textwidth}
\vspace{-1em}
\small\centering
\caption{Key figures of the dataset}\label{tbl:dataset}
\begin{tabular}{ll}
\toprule
\multicolumn{2}{c}{\emph{Time}} \\[0.5mm]
Period & 2000 to Q1 2012 \\
Resolution & Monthly \\
Snapshots & 154 Graphs \\
\midrule
\multicolumn{2}{c}{\emph{All graphs}} \\[0.5mm]
Nodes & 1.3 Million \\
Vertices & 6.9 Million \\
\midrule
\multicolumn{2}{c}{\emph{Final graph}} \\[0.5mm]
Nodes & 15 Thousand \\
Vertices & 80 Thousand \\
\midrule
\multicolumn{2}{c}{\emph{Raw ebuilds}} \\[0.5mm]
Format & SquashFS \\
Size & 239 MB (compressed) \\
 & 4.4 GB (uncompressed) \\
Files & 2,990,722 \\
\midrule
\multicolumn{2}{c}{\emph{Compressed graphs}} \\[0.5mm]
Format & Tar+XZ compressed GML \\
Size & 2 MB \\
\bottomrule
\end{tabular}
\end{wraptable}

@@

\section{Exploration of the Dataset}

\begin{figure}
\small\centering
\subfigure[Total number of packages]{\includegraphics[width=0.45\textwidth]{packageCountUnfiltered2.pdf}\label{fig:pkgsgrowth}}
\subfigure[Additions and removals]{\includegraphics[width=0.45\textwidth]{packageCountDeltaUnfiltered2.pdf}\label{fig:pkgsgrowthdelta}}
\caption{Growth of the Gentoo package database over time.}\label{fig:pkgsgrowth}
\end{figure}

@@

\begin{figure}
\small\centering
\subfigure[Dependencies per package]{\includegraphics[width=0.45\textwidth]{histo-out.pdf}\label{fig:dephisto-out}}
\subfigure[Dependers per package]{\includegraphics[width=0.45\textwidth]{histo-in.pdf}\label{fig:dephisto-in}}
\caption{Double logarithmic histograms of the number of incoming and outgoing dependencies per package.}
\end{figure}

@@

\begin{figure}
\small\centering
\includegraphics[clip,trim=0 0 1cm 10cm,width=\linewidth]{kde.pdf}
\caption{Internal dependencies of modules in the KDE project. Color represents the $k$-core measure. The graph edges have been bundled to improve readability.}\label{fig:kde2}
\end{figure}

@@

From the entire list of packages, a few well-known (at least according to the author) packages where selected. The selection criteria was that the package must not have existed before (around) 2004, because the Gentoo Portage database was still too immature then, and the package must have gained a considerable number of dependers since its introduction. In \ref{tbl:results}, we list some selected packages along with their parameters. In all cases the adjusted coefficient of determination $\overline{R}^2$ was more than $99\%$.

\begin{table}
\small\centering
\caption{Results of fitting the Bass model.}\label{tbl:results}
\begin{tabular}{lr@{ $\pm$}rr@{ $\pm$}rr@{ $\pm$}rr}
\toprule
Package & \multicolumn{2}{c}{$p$} & \multicolumn{2}{c}{$q$} & \multicolumn{2}{c}{$M$} & $\overline{R}^2$\\
\midrule
\texttt{git}         & 0.00 & 0.01    & 0.73 & 0.13   & 746 & 394 & 99.27\%\\
\texttt{libnotify}   & 0.05 & 0.08    & 0.72 & 0.30   & 103 &   9 & 99.23\%\\
\texttt{udev}        & 0.01 & 0.01    & 0.50 & 0.12   & 200 &  65 & 99.05\%\\
\texttt{cairo}       & 0.01 & 0.01    & 0.43 & 0.09   & 249 &  44 & 99.73\%\\
\texttt{libmad}      & 0.18 & 0.14    & 1.13 & 0.3    &  55 &   1 & 99.68\%\\
\texttt{libtheora}   & 0.11 & 0.09    & 0.63 & 0.21   &  32 &   1 & 99.75\%\\
\texttt{taglib}      & 0.22 & 0.03    & 0.04 & 0.06   &  62 &  12 & 99.40\%\\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}
\small\centering
\includegraphics[width=\linewidth]{BassFit-git2.pdf}
\vspace{-2em}
\caption{The imitation driven adoption of \texttt{git}.}\label{fig:git}
\vspace{-1.5em}
\end{figure}

@@

\begin{figure}
\small\centering
\includegraphics[width=\linewidth]{BassFit-libmad2.pdf}
\vspace{-2em}
\caption{The innovation driven adoption of \texttt{libmad}.}\label{fig:libmad}
\vspace{-1em}
\end{figure}

@@

\begin{figure}
\small\centering
\includegraphics[width=\linewidth]{BassFit-xulrunner-22.pdf}
\vspace{-2em}
\caption{The rise and decline of \texttt{xulrunner}.}\label{fig:xulrunner}
\vspace{-1em}
\end{figure}

@@

Excluding the blue dots from the data results in the Bass model fit from figure \ref{fig:xulrunner}. The fitness increases to $\overline{R}^2 =99.54\%$ and the parameters have tighter and reasonable confidence intervals. This is strong evidence that the initial adoption of the package is a Bass diffusion process. To explain the last part, the model should be extended with an obsolescence term.

\subsection{Moooore}

\begin{figure}
\small\centering
\caption[Dependee growth after package introduction]{The Bass curve fitted on a number of packages}
\label{fig:BassFits}
\subfigure[\texttt{libnotify}: $p=0.05$, $q=0.72$]{\includegraphics[width=0.45\textwidth]{BassFit-libnotify.pdf}}
\subfigure[\texttt{libtheora}: $p=0.11$, $q=0.63$]{\includegraphics[width=0.45\textwidth]{BassFit-libtheora.pdf}}
\subfigure[\texttt{taglib}: $p=0.22$, $q=0.04$]{\includegraphics[width=0.45\textwidth]{BassFit-taglib.pdf}}
\subfigure[\texttt{udev}: $p=0.01$, $q=0.50$]{\includegraphics[width=0.45\textwidth]{BassFit-udev.pdf}}
\subfigure[\texttt{cairo}: $p=0.005$, $q=0.35$]{\includegraphics[width=0.45\textwidth]{BassFit-cairo.pdf}}
\end{figure}

@@

\small\centering

@@

\begin{table}
\small\centering
\caption{The ten selected packages}\label{tbl:selected}
\begin{tabular}{rlp{20em}}
\toprule
Growth & Package & Description \\
\midrule
\raisebox{-.15em}{\includegraphics[height=.8em]{sparkline-34-dev-dotnet-gconf-sharp.pdf}} & \texttt{dev-dotnet/gconf-sharp} & GtkSharp's gconf module \\
\raisebox{-.15em}{\includegraphics[height=.8em]{sparkline-65-dev-haskell-cabal.pdf}}  & \texttt{dev-haskell/cabal} & Framework for packaging Haskell software \\
\raisebox{-.15em}{\includegraphics[height=.8em]{sparkline-218-dev-libs-libunique.pdf}}  & \texttt{dev-libs/libunique} & Library for writing single instance application \\
\raisebox{-.15em}{\includegraphics[height=.8em]{sparkline-77-dev-python-lxml.pdf}}  & \texttt{dev-python/lxml} & Python bindings for libxml2 and libxslt \\
\raisebox{-.15em}{\includegraphics[height=.8em]{sparkline-157-dev-python-simplejson.pdf}}  & \texttt{dev-python/simplejson} & JSON encoder/decoder for Python \\
\raisebox{-.15em}{\includegraphics[height=.8em]{sparkline-240-dev-vcs-git.pdf}}  & \texttt{dev-vcs/git} & The stupid content tracker \\
\raisebox{-.15em}{\includegraphics[height=.8em]{sparkline-242-dev-vcs-mercurial.pdf}}  & \texttt{dev-vcs/mercurial} & Scalable distributed SCM \\
\raisebox{-.15em}{\includegraphics[height=.8em]{sparkline-17-gnome-base-gnome-keyring.pdf}}  & \texttt{gnome-base/gnome-keyring} & Password and keyring managing daemon \\
\raisebox{-.15em}{\includegraphics[height=.8em]{sparkline-206-media-libs-libcanberra.pdf}} & \texttt{media-libs/libcanberra} & Portable sound event library \\
\raisebox{-.15em}{\includegraphics[height=.8em]{sparkline-143-x11-misc-xdg-utils.pdf}} & \texttt{x11-misc/xdg-utils} & Portland utils for interoperability \\
\bottomrule
\end{tabular}
\end{table}
% IDs = {34, 65, 218, 77, 157, 240, 242, 17, 206, 143}

@@

% 34-dev-dotnet-gconf-sharp:

@@

\begin{figure}
\small\centering
% 34, 65, 218, 77, 157, 240, 242, 17, 206, 143
\subfigure[\texttt{dev-dotnet/gconf-sharp}]{\includegraphics[width=0.45\textwidth]{BassFit-34-dev-dotnet-gconf-sharp.pdf}\label{fig:fit34}}
\subfigure[\texttt{dev-haskell/cabal}]{\includegraphics[width=0.45\textwidth]{BassFit-65-dev-haskell-cabal.pdf}\label{fig:fit65}}
\subfigure[\texttt{dev-libs/libunique}]{\includegraphics[width=0.45\textwidth]{BassFit-218-dev-libs-libunique.pdf}\label{fig:fit218}}
\subfigure[\texttt{dev-python/lxml}]{\includegraphics[width=0.45\textwidth]{BassFit-77-dev-python-lxml.pdf}\label{fig:fit77}}
\subfigure[\texttt{dev-python/simplejson}]{\includegraphics[width=0.45\textwidth]{BassFit-157-dev-python-simplejson.pdf}\label{fig:fit157}}
\subfigure[\texttt{dev-vcs/git}]{\includegraphics[width=0.45\textwidth]{BassFit-240-dev-vcs-git.pdf}\label{fig:fit240}}
\subfigure[\texttt{dev-vcs/mercurial}]{\includegraphics[width=0.45\textwidth]{BassFit-242-dev-vcs-mercurial.pdf}\label{fig:fit242}}
\subfigure[\texttt{gnome-base/gnome-keyring}]{\includegraphics[width=0.45\textwidth]{BassFit-17-gnome-base-gnome-keyring.pdf}\label{fig:fit17}}
\subfigure[\texttt{media-libs/libcanberra}]{\includegraphics[width=0.45\textwidth]{BassFit-206-media-libs-libcanberra.pdf}\label{fig:fit206}}
\subfigure[\texttt{x11-misc/xdg-utils}]{\includegraphics[width=0.45\textwidth]{BassFit-143-x11-misc-xdg-utils.pdf}\label{fig:fit143}}
\caption{Bass curve fits on ten randomly selected packages that met the criteria.}
\end{figure}

\begin{table}
\small\centering
\caption{Results of fitting the Bass model.}\label{tbl:results}
\begin{tabular}{lr@{ $\pm$}rr@{ $\pm$}rr@{ $\pm$}rr}
\toprule
Package & \multicolumn{2}{c}{$p$} & \multicolumn{2}{c}{$q$} & \multicolumn{2}{c}{$M$} & $\overline{R}^2$\\
\midrule
% 34, 65, 218, 77, 157, 240, 242, 17, 206, 143
\texttt{dev-dotnet/gconf-sharp}   & 0.167587 & 0.211648 & 0.754343 & 0.433141 & 21.283 & 0.484352 & 99.6148\%\\
\texttt{dev-haskell/cabal}        & 0.0554162 & 0.0732542 & 0.153744 & 0.379092 & 245.886 & 437.01 & 98.5521\%\\
\texttt{dev-libs/libunique}       & 0.0473548 & 0.0983485 & 0.136046 & 0.401718 & 286.948 & 731.387 & 98.5822\%\\
\texttt{dev-python/lxml}          & 0.00673774 & 0.00829268 & 0.48833 & 0.216921 & 52.883 & 52.4726 & 98.8237\%\\
\texttt{dev-python/simplejson}    & 0.0108121 & 0.0283649 & 0.463439 & 0.458178 & 97.1942 & 147.927 & 98.9801\%\\
\texttt{dev-vcs/git}              & 0.000415898 & 0.00512837 & 0.840506 & 0.143992 & 734.243 & 368.631 & 99.2386\%\\
\texttt{dev-vcs/mercurial}        & 0.00103413 & 0.00494549 & 0.516704 & 0.258352 & 173.8 & 480.637 & 98.2389\%\\
\texttt{gnome-base/gnome-keyring} & 0.0259038 & 0.0356738 & 0.833393 & 0.132449 & 41.5442 & 1.06264 & 99.6646\%\\
\texttt{media-libs/libcanberra}   & 0.0551051 & 0.116892 & 1.43593 & 0.438961 & 37.456 & 2.37536 & 99.6823\%\\
\texttt{x11-misc/xdg-utils}       & 0.0496807 & 0.0427185 & 0.257095 & 0.241258 & 114.925 & 126.964 & 99.5608\%\\
\bottomrule
\end{tabular}
\end{table}

@@

\section{Implications to Practice and Research}
